Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-04-13 manuscript.tex
Link to published version [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/48a8061369730c267ae98a1b6fbadf103db6cd4d.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/48a8061369730c267ae98a1b6fbadf103db6cd4d/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/744888012

A published version of this manuscript is available at \url{https://doi.org/10.1186/s12903-021-01551-x}.
This current version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/6d0a6402c44cb9745875171d2d33c37b4d7fe4be...a58577793380052c7fdf515ff2a5360b9e525391}{has been updated} with minor corrections compared to the submitted version.
These errors have been corrected in the proof-stage at BMC Oral Health and are \emph{not} present in the published version.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/a58577793380052c7fdf515ff2a5360b9e525391/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/a58577793380052c7fdf515ff2a5360b9e525391}{habi/zmk-tooth-cohort-method-manuscript@a585777}
on April 13, 2021.

>>>>

A published version of this manuscript is available at \url{https://doi.org/10.1186/s12903-021-01551-x}.
The version of the manuscript you see here \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/6d0a6402c44cb9745875171d2d33c37b4d7fe4be...48a8061369730c267ae98a1b6fbadf103db6cd4d}{has been updated} with minor corrections compared to the submitted version.
These errors have been corrected in the proof-stage at BMC Oral Health and are \emph{not} present in the published version.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/48a8061369730c267ae98a1b6fbadf103db6cd4d/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/48a8061369730c267ae98a1b6fbadf103db6cd4d}{habi/zmk-tooth-cohort-method-manuscript@48a8061}
on April 13, 2021.
